Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design

### 2016-09-20 MSR-design.tex
Reduce width of Cammi boundary condition figure.
Add ARFC MSRE reactor design step list.

\title{Advanced Reactor Fuel cycle Molten Salt Reactor Design}
\author{Alexander Lindsay, Katy Huff, Andrei Rykhlevskii} % As you author additions/changes, add
                                      % your name here!!!

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{Cammi_simplification_1.png}
  \caption{Cammi's simplification of MSBR's geometry. \cite{cammi_multi-physics_2011}}
  \label{fig:simlification}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{Cammi_simplification_2.png}
  \caption{(b) Fluid flow and heat transfer boundary conditions; (c) neutron flux and DNP boundary conditions. \cite{cammi_multi-physics_2011}}
  \label{fig:simlification-2}
\end{figure}

>>>>

\newcommand{\code}[1]{\texttt{#1}}

\title{Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design}
\author{Alexander Lindsay, Katy Huff, Andrei Rykhlevskii} % As you author additions/changes, add
                                      % your name here!!!

@@

\subsection{ARFC MSRE Model Design Plan}

\begin{enumerate}
\item Test whether \code{gmsh} can generate heterogeneous 3D mesh structure
  like that in the actual MSRE geometry.
\item For expected range of temperatures and some defined sequence of
  temperature step sizes, generate table of few-group neutronics cross sections
  with \code{SERPENT}.
  \begin{itemize}
    \item If \code{gmsh}, or that failing \code{cubit}, is capable of generating
      heterogeneous grid, we can generate unique cross regions for each region
    \item If we cannot generate heterogeneous grid, we will have to homogenize
      the cross sections similar to what is done in
      \cite{kophazi_development_????}.
  \end{itemize}
\item Armed with tables for quick interpolation of cross sections, we should be
  able to perform coupled calculations for neutron density and
  temperature.
  \begin{itemize}
    \item As a first pass, the fuel salt flow velocity can be a user input as
      opposed to a non-linear variable that is a function of temperature.
    \item We will need to decide whether neutron and temperature calculations
      should be performed on the same grid, and in transient calculations
      whether those two fields should be updated on the same step-size.
      \begin{itemize}
        \item If not using the same grid and/or step-size, the neutronic and
          temperature calculations will need to be split into their own
          applications and coupling will have to be performed using the MOOSE
          multi-app system.
      \end{itemize}
  \end{itemize}
\end{enumerate}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{Cammi_simplification_1.png}
  \caption{Cammi's simplification of MSBR's geometry. \cite{cammi_multi-physics_2011}}
  \label{fig:simlification}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{Cammi_simplification_2.png}
  \caption{(b) Fluid flow and heat transfer boundary conditions; (c) neutron flux and DNP boundary conditions. \cite{cammi_multi-physics_2011}}
  \label{fig:simlification-2}
\end{figure}
